---
title: "Final_Project_Presentation"
author: "Santosh Vinnakota"
date: "06/08/2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview


This is an RStudio shiny application developed as a part of week 4 project in the Developing Data Products course in Coursera Data Science Specialization track. The application is dynamic line chart based on the selection

The project includes:

Radio button 



## Application Contains

Form of Input used: Radio Button

Reactive output Line chart displayed based on the selections

The server.R and ui.R codes are posted on github at:https://github.com/SuryaV21/Test-Repo/tree/gh-pages/Week_4_Project

This app is hosted at: https://svinnakota.shinyapps.io/week_4/

## Shiny Code

library(shiny)


shinyUI(fluidPage(

    # Application title
    titlePanel("Old Faithful Geyser Data"),
    
    radioButtons('Test', 'choose selection', choices = c('mpg','disp'), selected = 'mpg',
                 inline = FALSE, width = NULL, choiceNames = NULL,
                 choiceValues = NULL)
    ,    verbatimTextOutput("ncount_2")
    ,plotlyOutput("graph")
    
))

library(shiny)


shinyServer(function(input, output) {

    library(plotly)
   
    output$ncount_2 <- renderPrint({
        ncount <- input$Test
        paste(ncount,"100",sep="_")
    })
    output$graph <- renderPlotly({

       if (input$Test == 'mpg') {
           
           plot_ly(mtcars, x= ~wt, y = ~mpg,type = "scatter", mode = "lines+markers", color = ~as.factor(cyl))
       }
       
        else {
            plot_ly(mtcars, x= ~wt, y = ~disp,type = "scatter", mode = "lines+markers", color = ~as.factor(cyl))  
        }
        
    })

})




## output

``` {r}
library(plotly)
plot_ly(mtcars, x= ~wt, y = ~mpg,type = "scatter", mode = "lines+markers", color = ~as.factor(cyl))
```



