---
title: "Predictive Machine Learning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Reading the required libraried and data from 2 different sources

```{r }
setwd("D://Analytics//Data Sciences//Practical Machine Learning")
library(caret);library(rattle); library(rpart)
```


```{r Loading data}
training <- read.csv("pml-training.csv")
testing <- read.csv("pml-testing.csv")
dim(training);dim(testing)
```
 Looking at the train data
```{r glance at train data}
str(training)
```
 If the column data is less than 50% it is diffcult to impute. So we are looking the columns which are having more than 70% nulls

``` {r Remove columns if contains more than 70% nulls}
NullColumns <- which(colSums(is.na(training) |training=="")>0.7*dim(training)[1]) 
training<- training[,-NullColumns]
```
Removing 7 variables as we do not need that information 

```{r removing unneccessary variables}
training <- training[,-c(1:7)]
## Data After removing nulls and non-important columns
dim(training)
```

To check the efficiancy of the model, we are splitting the training data into train and test before implementing on actual test data

```{r Splitting train data into train and test data}
set.seed(12345)
inTrain <- createDataPartition(training$classe, p=0.75, list=FALSE)
train <- training[inTrain,]
test <- training[-inTrain,]
dim(train);dim(test)
```
We will check the accuracy by applying multiple models. Below is Classification Model

```{r Applying Classification model}
#RModel <- rpart(classe ~ ., data=train, method="class")

tcontrol <- trainControl(method="cv", number=5)
CTModel <- train(classe~., data=train, method="rpart", trControl=tcontrol)
fancyRpartPlot(CTModel$finalModel)
```

Prdiction of Test data using Cross-Validation Model

```{r prediction for test data using CV model}
testpred <- predict(CTModel,newdata=test)

confMatCT <- confusionMatrix(test$classe,testpred)

confMatCT$table; confMatCT$overall[1]

```

Random Forest Model prediction using Train data

```{r Predicting with Random Forests}
tcontrol <- trainControl(method="cv", number=5)
RFModel <- train(classe~., data=train, method="rf", trControl=tcontrol, verbose=FALSE)

print(RFModel)

```
Test data model prediction


```{r test prediction}
testpred <- predict(RFModel,newdata=test)

confMatRF <- confusionMatrix(test$classe,testpred)
confMatRF$overall[1];RFModel$finalModel$classes

```
Gradient Boosting model

```{r Prediction with Gradient Boosting}
tcontrol <- trainControl(method="cv", number=5)
GBModel <- train(classe~., data=train, method="gbm", trControl=tcontrol, verbose=FALSE)

print(GBModel)

```

```{r test prediction with Gradient Boosting}
testpred <- predict(GBModel,newdata=test)

confMatGBM <- confusionMatrix(test$classe,testpred)
confMatGBM$table

```
Applying better model 

```{r Applying Final model on original test data}

testingpred <- predict(RFModel, newdata=testing)
testingpred

```